Modular transmission line probes for microfluidic nuclear magnetic resonance spectroscopy and imaging

### 2019-02-08 ms5n17-tlp-mn-180216-001.tex
cover letter

In this paper we present a novel modular probe designed for generic
microfluidic-NMR experiments. The design is based on a transmission line
detector~\cite{stripline_jan,gream_2016} using inexpensive
printed circuit board (PCB) technology. A modular design ensures that detectors of
different geometry and size can be easily exchanged.
The NMR detector (including the tuning and matching circuit) is connected to the probe
skeleton through detachable connectors. Modularity of the probe not only allows
fast optimisation of the detector but also facilitates the use of dedicated detectors
for different microfluidic devices on a single probe base.
Once the probe base is in place, additional detectors can be manufactured
within 2-3 days for less than $\sim$200 $\geneuro$.
The probe is designed for proton detected double resonance.
The second channel can be tuned to different nuclei such as $^{13}$C, $^{15}$N, or
$^{31}$P. The probe skeleton is made almost entirely from easily obtainable raw materials
such as aluminium profiles of standard size, with only a small number of
custom-machined parts holding the structure together.
Detailed construction drawings and a complete set of CAD files is
available for download at \url{https://github.com/marcel-utz/modular-microfluidic-probe}.
The planar geometry of the detector accommodates exchangeable microfluidic devices
which can be designed freely for specific experimental requirements as long as the
overall shape of the device is maintained. \fig{fig:rf-device-assembly} shows the microfluidic device and the detector with their relative orientation.

@@

Microfluidic devices are made from inexpensive PMMA sheets by laser cutting and
thermal bonding, as described in detail elsewhere \cite{yilmaz_bonding}.
Briefly, the devices consist of a 0.5~mm thick middle layer between a  top and
bottom layer of 0.2~mm thickness each. The sample chamber and fluidic network
are cut into the middle layer. The fluidic network on the device can be designed
freely as long as the overall shape of the device is preserved, and the location
of the sample chamber is maintained.

@@

Using simple microfluidic devices made from PMMA sheets by laser cutting,
spectral resolution around 0.005~ppm is achieved in proton spectra at
600~MHz. This is sufficient for primary metabolic studies, but some
applications could benefit from better resolution. The probe has already been
used for various  experiments including reaction monitoring~\cite{Fang-2018},
micro-imaging of mouse liver tissue slices, and metabolic studies of
mammalian cells. The probe is designed for double resonance, and
acqusition of proton-detected heteronuclear correlation experiments
has been demonstrated for small molecules as well as proteins.
In the future we intend to add a field-frequency lock channel,
as well as additional functionality for advanced microfluidic perfusion with temperature and flow control.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Acknowledgement}
This research was supported by the "TISuMR" project,
funded through "Future and Emerging Technologies" (FETOPEN)
call of the EU Horizon 2020 research framework. The authors would like to
thank Mr.~William Hale for help with
making microfluidic devices, Dr.~Katrin Deinhardt for providing
the mouse liver tissue, Dr.~Bishnubrata Patra for tissue slicing and Dr.~J\"{o}rn Werner for providing the
labelled ubiquitin sample and for his support in the acquisition
and processing of the HSQC spectrum.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage
\bibliographystyle{unsrt}
\bibliography{science}
\end{document}

>>>>

In this paper we present a novel modular probe designed for generic
microfluidic-NMR experiments. The design is based on a transmission line
detector~\cite{stripline_jan,gream_2016} using inexpensive
printed circuit board (PCB) technology. A modular design ensures that detectors of
different geometry and size can be easily exchanged.
The NMR detector (including the tuning and matching circuit) is connected to the probe
skeleton through detachable connectors. Modularity of the probe not only allows
fast optimisation of the detector but also facilitates the use of dedicated detectors
for different microfluidic devices on a single probe base.
Once the probe base is in place, additional detectors can be manufactured
within 2-3 days for less than $\sim$200 $\geneuro$.
The probe is designed for proton detected double resonance.
The second channel can be tuned to different nuclei such as $^{13}$C, $^{15}$N, or
$^{31}$P. The probe skeleton is made almost entirely from easily obtainable raw materials
such as aluminium profiles of standard size, with only a small number of
custom-machined parts holding the structure together.
Detailed construction drawings and a complete set of CAD files is
available for download at \url{https://github.com/marcel-utz/modular-microfluidic-probe}.
The planar geometry of the detector accommodates exchangeable microfluidic devices
which can be designed freely for specific experimental requirements as long as the
overall shape of the device is maintained. \fig{fig:rf-device-assembly} shows the microfluidic device and the detector with their relative positioning.

@@

Microfluidic devices are made from inexpensive PMMA sheets by laser cutting and
thermal bonding, as described in detail elsewhere \cite{yilmaz_bonding}.
Briefly, the devices consist of a 0.5~mm thick middle layer between a  top and
bottom layer of 0.2~mm thickness each. The sample chamber and fluidic network
are cut into the middle layer. The fluidic network on the device can be designed
freely as long as the overall shape of the device is preserved, and the location
of the sample chamber is maintained. The volume of the sample chamber is 2.5~$\mu$l which can be increased or decreased according to the experimental requirments.

@@

Using simple microfluidic devices made from PMMA sheets by laser cutting,
spectral resolution around 0.005~ppm is achieved in proton spectra at
600~MHz. This is sufficient for primary metabolic studies, but some
applications could benefit from better resolution. The probe has already been
used for various  experiments including reaction monitoring~\cite{Fang-2018},
micro-imaging of mouse liver tissue slices, and metabolic studies of
mammalian cells. The probe is designed for double resonance, and
acquisition of proton-detected heteronuclear correlation experiments
has been demonstrated for small molecules as well as proteins.
In the future we intend to add a field-frequency lock channel,
as well as additional functionality for advanced microfluidic perfusion with temperature and flow control.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Acknowledgement}
This research was supported by the "TISuMR" project,
funded through "Future and Emerging Technologies" (FETOPEN)
call of the EU Horizon 2020 research framework. The authors would like to
thank Mr.~William Hale for help with
making microfluidic devices, Dr.~Katrin Deinhardt for providing
the mouse liver tissue, Dr.~Bishnubrata Patra for tissue slicing and Dr.~J\"{o}rn Werner for providing the
labelled ubiquitin sample and for his support in the acquisition
and processing of the HSQC spectrum.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage
\bibliographystyle{unsrt}
\bibliography{science}
\end{document}
